Next Trippy Structures\thanks{Supported by organization x.}

### 2019-02-19 paper.tex
Nieves comments
Fix network figure
Experimenting with tables

These are the main elements from our model:
\begin{itemize}
    \item A \textbf{stop\_place} is a physical stop with a location, on which several lines may make stops.
    \item A \textbf{line} is an ordered sequence of stop places that can be traveled by a transport vehicle, such as a bus or a train. It only considers one direction. For this reason, there is often a different and complementary line for the opposite direction.
    \item A \textbf{journey} is a single traversal of a transport vehicle over a line. It can be seen as a vehicle trip, instead of a user trip.
    \item A \textbf{stage} is formed by a boarding from a stop and alighting to another from the same single line and journey.
    \item An \textbf{user\_trip} is a concatenation of several stages, until the final destination (alighting stop of the last stage) is reached.
\end{itemize}

@@

The following is a non-comprehensive list of query types that can be efficiently solved with the structures proposed in this work:
\begin{itemize}
    \item \texttt{board\_X$_{LT}$} Number of times that stop X is boarded, optionally restricting to a line L and a time range T.
    \item \texttt{alight\_X$_{LT}$} Number of times that stop X is alighted, optionally restricting to a line L and a time range T.
    \item \texttt{start\_X$_{LT}$} User trips starting at a stop X, optionally restricting to a line L and a time range T.
    \item \texttt{end\_X$_{LT}$} User trips ending at a stop X, optionally restricting to a line L and a time range T.
    \item \texttt{switch\_X$_{LT}$} Number of trips in which the stop X was used to switch lines, optionally restricting to a line L and a time range T.
    \item \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} User trips that originate at stop X to end at stop Y, both being optionally restricted to a line and time range.
    \item \texttt{board\_L$_T$}  Number of times that line L is boarded, optionally restricting to a time range T.
    \item \texttt{alight\_L$_T$} Number of times that line L is alighted, optionally restricting to a time range T.
    \item \texttt{start\_L$_T$} User trips starting at any stop from the line L, optionally restricting to a time range T.
    \item \texttt{end\_L$_T$} User trips ending at any stop from the line L, optionally restricting to a time range T.
    \item \texttt{board\_T} Number of times a user boards within a time range T.
    \item \texttt{alight\_T} Number of times a user alights within a time range T.
    \item \texttt{start\_T} User trips starting within a time range T.
    \item \texttt{end\_T} User trips ending within a time range T.
    \item \texttt{load\_X$_{LT}$} The average number of passengers traveling from the stop X to its next stop in the line L within the time range T. Can also be seen as the average load of a transport vehicle.

@@

\subsection{Comparing \acumm and \ctr}
\label{sec:comp}
Better show this after they have been both explained...

@@

>>>>

These are the main elements from our model:
\begin{itemize}
    \item A \textbf{stop\_place} is a physical stop with a location, on which several lines may make stops.
    \item A \textbf{line} is an ordered sequence of stop places that can be traveled by a transport vehicle, such as a bus or a train. It only considers one direction. For this reason, there is often a different and complementary line for the opposite direction, as shown in the Figure~\ref{fig:example_network}.
    \item A \textbf{journey} is a single traversal of a transport vehicle over a line. It can be seen as a vehicle trip, instead of a user trip.
    \item A \textbf{stage} is formed by a boarding from a stop and alighting to another from the same single line and journey.
    \item An \textbf{user\_trip} is a concatenation of several stages, until the final destination (alighting stop of the last stage) is reached.
\end{itemize}

@@

The following is a non-comprehensive list of query types that can be efficiently solved with the structures proposed in this work:
\marginpar{\tiny Nieves: Reorganizar seguindo a clasificación}
\begin{itemize}
    \item \texttt{board\_X$_{LT}$} Number of times that stop X is boarded, optionally restricting to a line L and a time range T.
    \item \texttt{alight\_X$_{LT}$} Number of times that stop X is alighted, optionally restricting to a line L and a time range T.
    \item \texttt{start\_X$_{LT}$} User trips starting at a stop X, optionally restricting to a line L and a time range T.
    \item \texttt{end\_X$_{LT}$} User trips ending at a stop X, optionally restricting to a line L and a time range T.
    \item \texttt{switch\_X$_{LT}$} Number of trips in which the stop X was used to switch lines, optionally restricting to a line L and a time range T.
    \item \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} User trips that originate at stop X to end at stop Y, both being optionally restricted to a line and time range.
    \item \texttt{board\_L$_T$}  Number of times that line L is boarded, optionally restricting to a time range T.
    \item \texttt{alight\_L$_T$} Number of times that line L is alighted, optionally restricting to a time range T.
    \item \texttt{start\_L$_T$} User trips starting at any stop from the line L, optionally restricting to a time range T.
    \item \texttt{end\_L$_T$} User trips ending at any stop from the line L, optionally restricting to a time range T.
    \item \texttt{board\_T} Number of times a user boards within a time range T.
    \item \texttt{alight\_T} Number of times a user alights within a time range T.
    \item \texttt{start\_T} User trips starting within a time range T.
    \item \texttt{end\_T} User trips ending within a time range T.
    \item \texttt{load\_X$_{LT}$} The average number of passengers traveling from the stop X to its next stop in the line L within the time range T. Can also be seen as the average load of a transport vehicle.

@@

\subsection{Comparing \acumm and \ctr}
\label{sec:comp}
Better show this after they have been both explained... \marginpar{\tiny Include TTCTR in the table}

@@

\begin{table}
\caption{Comparison of start\_X$_{LT}$ queries, with all variants}
\label{tab:queries}
\begin{tabular}{|r|r|r|r|r|r|}
\hline
$t_{\Psi}$ & \texttt{WMJ} & \texttt{start\_X} & \texttt{start\_X$_{L}$} & \texttt{start\_X$_{T}$} & \texttt{start\_X$_{LT}$} \\
\hline
32 & RG32 & 4.20 & 4.16 & 18.52 & 8.22 \\
32 & RRR32 & 4.18 & 4.18 & 21.01 & 9.43 \\
32 & RRR64 & 4.21 & 4.15 & 21.70 & 9.65 \\
32 & RRR128 & 4.18 & 4.15 & 23.20 & 10.22 \\
128 & RG32 & 6.96 & 6.94 & 25.05 & 10.68 \\
128 & RRR32 & 6.96 & 6.94 & 27.44 & 11.78 \\
128 & RRR64 & 6.95 & 6.95 & 28.05 & 12.04 \\
128 & RRR128 & 6.94 & 6.94 & 29.64 & 12.62 \\
512 & RG32 & 17.01 & 16.85 & 51.36 & 21.13 \\
512 & RRR32 & 17.03 & 16.92 & 53.78 & 21.80 \\
512 & RRR64 & 17.05 & 16.86 & 54.43 & 22.01 \\
512 & RRR128 & 17.00 & 17.08 & 55.88 & 22.65 \\
\hline
\end{tabular}

\begin{tabular}{|r|r|r|r|r|r|r|}
\hline
$t_{\Psi}$ & \texttt{WML} & \texttt{WMJ} & \texttt{start\_X} & \texttt{start\_X$_{L}$} & \texttt{start\_X$_{T}$} & \texttt{start\_X$_{LT}$} \\
\hline
32 & RG32 & RG32 & 3.41 & 5.85 & 20.39 & 11.58 \\
32 & RG32 & RRR32 & 3.44 & 5.82 & 23.15 & 12.99 \\
32 & RG32 & RRR64 & 3.42 & 5.82 & 23.70 & 13.22 \\
32 & RG32 & RRR128 & 3.44 & 5.83 & 25.09 & 13.77 \\
32 & RRR32 & RG32 & 3.42 & 5.52 & 20.72 & 11.68 \\
32 & RRR32 & RRR32 & 3.42 & 5.49 & 23.27 & 12.93 \\
32 & RRR32 & RRR64 & 3.43 & 5.45 & 23.75 & 13.17 \\
32 & RRR32 & RRR128 & 3.42 & 5.49 & 25.16 & 13.71 \\
32 & RRR64 & RG32 & 3.44 & 5.61 & 21.16 & 11.70 \\
32 & RRR64 & RRR32 & 3.46 & 5.59 & 23.66 & 13.01 \\
32 & RRR64 & RRR64 & 3.44 & 5.58 & 24.33 & 13.26 \\
32 & RRR64 & RRR128 & 3.41 & 5.63 & 25.67 & 13.78 \\
32 & RRR128 & RG32 & 3.50 & 6.05 & 22.24 & 12.09 \\
32 & RRR128 & RRR32 & 3.41 & 6.15 & 24.62 & 13.34 \\
32 & RRR128 & RRR64 & 3.42 & 7.20 & 25.44 & 13.64 \\
32 & RRR128 & RRR128 & 3.43 & 6.11 & 26.66 & 14.16 \\
128 & RG32 & RG32 & 6.34 & 9.43 & 22.65 & 14.02 \\
128 & RG32 & RRR32 & 6.30 & 8.55 & 25.45 & 15.37 \\
128 & RG32 & RRR64 & 6.39 & 8.53 & 26.00 & 15.66 \\
128 & RG32 & RRR128 & 6.33 & 8.53 & 27.36 & 16.21 \\
128 & RRR32 & RG32 & 6.30 & 8.28 & 22.98 & 14.07 \\
128 & RRR32 & RRR32 & 6.46 & 8.23 & 25.45 & 15.29 \\
128 & RRR32 & RRR64 & 6.32 & 8.29 & 26.05 & 15.55 \\
128 & RRR32 & RRR128 & 6.31 & 8.29 & 27.43 & 16.10 \\
128 & RRR64 & RG32 & 6.33 & 8.54 & 23.53 & 14.22 \\
128 & RRR64 & RRR32 & 6.30 & 8.54 & 25.83 & 15.38 \\
128 & RRR64 & RRR64 & 6.31 & 8.46 & 26.46 & 15.61 \\
128 & RRR64 & RRR128 & 6.30 & 8.48 & 27.82 & 16.18 \\
128 & RRR128 & RG32 & 6.31 & 8.91 & 24.52 & 14.52 \\
128 & RRR128 & RRR32 & 6.30 & 8.94 & 27.09 & 15.85 \\
128 & RRR128 & RRR64 & 6.30 & 8.93 & 27.71 & 16.04 \\
128 & RRR128 & RRR128 & 6.36 & 8.91 & 28.95 & 16.55 \\
512 & RG32 & RG32 & 16.32 & 18.64 & 32.55 & 24.02 \\
512 & RG32 & RRR32 & 16.29 & 18.63 & 35.31 & 25.44 \\
512 & RG32 & RRR64 & 16.28 & 18.65 & 35.81 & 25.61 \\
512 & RG32 & RRR128 & 16.28 & 18.64 & 37.31 & 26.22 \\
512 & RRR32 & RG32 & 17.37 & 19.01 & 33.22 & 24.39 \\
512 & RRR32 & RRR32 & 16.33 & 18.38 & 35.44 & 26.38 \\
512 & RRR32 & RRR64 & 16.29 & 18.42 & 36.10 & 25.64 \\
512 & RRR32 & RRR128 & 16.40 & 18.39 & 37.35 & 26.23 \\
512 & RRR64 & RG32 & 16.30 & 18.59 & 33.50 & 24.27 \\
512 & RRR64 & RRR32 & 16.30 & 18.56 & 35.83 & 25.48 \\
512 & RRR64 & RRR64 & 16.32 & 18.57 & 36.60 & 25.72 \\
512 & RRR64 & RRR128 & 16.35 & 18.66 & 37.82 & 26.29 \\
512 & RRR128 & RG32 & 16.33 & 19.02 & 34.69 & 24.68 \\
512 & RRR128 & RRR32 & 16.30 & 19.04 & 36.95 & 25.81 \\
512 & RRR128 & RRR64 & 16.33 & 19.03 & 37.56 & 26.04 \\
512 & RRR128 & RRR128 & 16.27 & 19.02 & 38.89 & 26.62 \\

\hline
\end{tabular}
\end{table}
